---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
devtools::load_all()
```

# sehrnett

<!-- badges: start -->
<!-- badges: end -->

The goal of sehrnett is to provide a nice (and fast) interface to [Princeton's WordNet](https://wordnet.princeton.edu/). Unlike the original [wordnet package](https://cran.r-project.org/web/packages/wordnet/index.html) (Feinerer et al., 2020), you don't need to install WordNet and / or setup rJava.

The data is not included in the package. A function will be provided later to download the data (~100M Zipped, ~400M Unzipped) from the Internet, if such data is not available. Please make sure you agree with the [WordNet License](https://wordnet.princeton.edu/license-and-commercial-use).

## Installation

``` r
devtools::install_github("chainsawriot/sehrnett")
```

## Example

This is a basic example which shows you how to solve a common problem:

```r
library(sehrnett)
```

```{r}
search_lemma("nice")
```

```{r}
search_lemma("nice", pos = "n")
```
