---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
devtools::load_all()
```

# sehrnett

<!-- badges: start -->
<!-- badges: end -->

The goal of sehrnett is to provide a nice (and fast) interface to [Princeton's WordNet](https://wordnet.princeton.edu/). Unlike the original [wordnet package](https://cran.r-project.org/web/packages/wordnet/index.html) (Feinerer et al., 2020), you don't need to install WordNet and / or setup rJava.

The data is not included in the package. The package will download the data (~100M Zipped, ~400M Unzipped) from the Internet, if such data is not available. Please make sure you agree with the [WordNet License](https://wordnet.princeton.edu/license-and-commercial-use).

## Installation

``` r
devtools::install_github("chainsawriot/sehrnett")
```

## Example

The most basic function is `get_lemmas`. It generates basic information about the lemmas you provided.

```r
library(sehrnett)
```

```{r}
get_lemmas(c("very", "nice"))
```

```{r}
get_lemmas("nice")
```

```{r}
get_lemmas("nice", pos = "n")
```

## A practical example

For example, you want to know the synonyms of the word "nuance" (very important for academic writing). You can first search using the lemma "nuance" with `get_lemmas`.

```{r}
res <- get_lemmas("nuance")
res
```

There could be multiple word senses and you need to choose which word sense you want to convey. But in this case, there is only one. You can then search for the `synsetid` (cognitive synonym identifier) of that word sense.

```{r}
# get_synonyms() is a wrapper to get_synsetids
get_synsetids(res$synsetid[1])
```

## Chainablilty

All `get_` functions are chainable by using the magrittr pipe operator.

```{r}
c("switch off") %>% get_lemmas(pos = "v") %>% get_synonyms
```
